% ============================================================================
% SUPPLEMENTARY MATERIALS: POLYPHARMACY RISK ASSESSMENT AND ALTERNATIVE THERAPY
% ============================================================================

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{float}
\usepackage{longtable}
\usepackage{xcolor}
\geometry{margin=1in}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

% Suppress automatic section numbering (use manual S6, S7, etc.)
\setcounter{secnumdepth}{0}

\begin{document}

\begin{center}
\Large\textbf{Supplementary Materials (Continued)}\\ [0.5em]
\normalsize Polypharmacy Risk Assessment and Alternative Therapy Recommendation
\end{center}

% ============================================================================
\section{S6: Polypharmacy Risk Index (PRI) Derivation}
% ============================================================================

\subsection{Network-Based Risk Metrics}

The Polypharmacy Risk Index integrates four complementary network centrality measures that capture different aspects of drug interaction risk within the DDI knowledge graph.

\subsubsection{Degree Centrality}

Degree centrality captures the raw interaction burden of a drug:

\begin{equation}
C_{\text{degree}}(d) = \frac{\text{deg}(d)}{N - 1}
\end{equation}

where $\text{deg}(d)$ is the number of edges connected to drug $d$ in the DDI network and $N$ is the total number of drugs. This metric identifies drugs with high interaction potential.

\subsubsection{Weighted Degree Centrality}

Weighted degree incorporates severity information:

\begin{equation}
C_{\text{weighted}}(d) = \frac{\sum_{j \in \Gamma(d)} w_{dj}}{\sum_{i,j} w_{ij}}
\end{equation}

where $\Gamma(d)$ is the set of neighbors of drug $d$ and $w_{dj}$ is the severity weight of the interaction between $d$ and $j$ (Contraindicated: 10.0, Major: 7.0, Moderate: 4.0, Minor: 1.0).

\subsubsection{Betweenness Centrality}

Betweenness centrality identifies drugs that serve as bridges in risk propagation:

\begin{equation}
C_{\text{betweenness}}(d) = \sum_{s \neq d \neq t} \frac{\sigma_{st}(d)}{\sigma_{st}}
\end{equation}

where $\sigma_{st}$ is the number of shortest paths between drugs $s$ and $t$, and $\sigma_{st}(d)$ is the number of those paths passing through drug $d$.

\subsubsection{Severity Profile Score}

The severity profile quantifies the proportion of high-risk interactions:

\begin{equation}
S(d) = \frac{|\{j : (d,j) \in E \land \text{severity}(d,j) \in \{\text{Contraindicated}, \text{Major}\}\}|}{|\{j : (d,j) \in E\}|}
\end{equation}

\subsection{Weight Optimization}

The PRI weights (0.25, 0.30, 0.20, 0.25) were optimized through grid search to maximize correlation with clinical severity assessments while maintaining balanced contribution from each metric. The weighted degree component receives the highest weight (0.30) as it most directly captures clinically significant interactions.

\subsection{PRI Distribution Statistics}

\begin{table}[H]
\centering
\caption{PRI Score Distribution Statistics Across All Drugs}
\label{tab:pri_stats}
\begin{tabular}{lr}
\toprule
\textbf{Statistic} & \textbf{Value} \\
\midrule
Mean & 0.342 \\
Median & 0.298 \\
Standard Deviation & 0.186 \\
Interquartile Range & 0.245 \\
Skewness & 0.824 (right-skewed) \\
Kurtosis & 2.91 \\
Minimum & 0.000 \\
Maximum & 0.892 \\
\bottomrule
\end{tabular}
\end{table}

% ============================================================================
\section{S7: Rule-Based Substitution Framework}
% ============================================================================

\subsection{Candidate Selection Rules}

The recommendation system employs a rule-based filtering approach to identify therapeutic alternatives. Alternative drugs must share the same ATC Level-3 code as the original drug, ensuring pharmacological equivalence within the same therapeutic subgroup.

\begin{table}[H]
\centering
\caption{Candidate Selection Rules}
\label{tab:candidate_rules}
\begin{tabular}{lp{10cm}}
\toprule
\textbf{Rule} & \textbf{Description} \\
\midrule
ATC Match & Alternative must share ATC Level-3 code with original drug \\
Exclusion & No contraindicated interactions with current regimen drugs \\
Presence & Alternative must exist in the knowledge graph with documented interactions \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Alternative Recommendation Score (ARS)}

Candidates passing the filtering criteria are ranked by the Alternative Recommendation Score (ARS):

\begin{equation}
\text{ARS}(d_{\text{alt}}) = 0.70 \cdot \underbrace{\frac{\sum_{d_i \in R} \left( w(d_{\text{orig}}, d_i) - w(d_{\text{alt}}, d_i) \right)}{W_{\text{max}}}}_{\text{Normalized Severity Reduction}} + 0.30 \cdot \underbrace{\left( \text{PRI}(d_{\text{orig}}) - \text{PRI}(d_{\text{alt}}) \right)}_{\text{PRI Improvement}}
\end{equation}

where $R$ is the set of other drugs in the current regimen, $w(d_a, d_b)$ is the severity weight of the interaction between drugs $d_a$ and $d_b$ (or 0 if no interaction exists), and PRI is the Polypharmacy Risk Index.

The normalization constant $W_{\text{max}} = 10 \cdot |R|$ represents the maximum possible severity reduction, where 10 is the weight of a Contraindicated interaction and $|R|$ is the number of other drugs in the regimen.

\subsection{Severity Weights for ARS Calculation}

\begin{table}[H]
\centering
\caption{Severity Weights for ARS Calculation}
\label{tab:severity_weights}
\begin{tabular}{lr}
\toprule
\textbf{Severity Level} & \textbf{Weight} \\
\midrule
Contraindicated & 10.0 \\
Major & 7.0 \\
Moderate & 4.0 \\
Minor & 1.0 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{ARS Score Components}

\begin{table}[H]
\centering
\caption{ARS Score Component Interpretation}
\label{tab:ars_components}
\begin{tabular}{llp{7cm}}
\toprule
\textbf{Component} & \textbf{Weight} & \textbf{Interpretation} \\
\midrule
Severity Reduction & 0.70 & Normalized improvement in interaction severity with current regimen (0-1 scale) \\
PRI Improvement & 0.30 & Reduction in global network risk (0-1 scale) \\
\bottomrule
\end{tabular}
\end{table}

The 0.70/0.30 weighting prioritizes immediate regimen safety (severity reduction) while ensuring network-level risk contributes meaningfully to ranking.

% ============================================================================
\section{S8: Algorithm Pseudocode}
% ============================================================================

\subsection{PRI Computation}

\textbf{Input:} DDI Knowledge Graph $G$, drug regimen $R$

\textbf{Output:} PRI scores for each drug

\begin{enumerate}
    \item For each drug $d \in R$:
    \begin{enumerate}
        \item Compute degree centrality $C_{\text{degree}}(d)$
        \item Compute weighted degree $C_{\text{weighted}}(d)$ using severity weights
        \item Compute betweenness centrality $C_{\text{betweenness}}(d)$
        \item Compute severity profile $S(d)$ = fraction of severe interactions
        \item $\text{PRI}(d) = 0.25 \cdot C_{\text{degree}} + 0.30 \cdot C_{\text{weighted}} + 0.20 \cdot C_{\text{betweenness}} + 0.25 \cdot S$
    \end{enumerate}
    \item Return PRI scores
\end{enumerate}

\subsection{ARS Recommendation}

\textbf{Input:} Current regimen $R$, target drug $d_{\text{orig}}$, Knowledge Graph $G$

\textbf{Output:} Ranked list of alternatives with ARS scores

\begin{enumerate}
    \item Find candidates sharing ATC Level-3 code with $d_{\text{orig}}$
    \item Set $W_{\text{max}} = 10 \cdot |R \setminus \{d_{\text{orig}}\}|$
    \item For each candidate $d_{\text{alt}}$:
    \begin{enumerate}
        \item Skip if contraindicated with any drug in $R$
        \item Compute severity reduction: $\Delta S = \sum_{d_i \in R}(w(d_{\text{orig}}, d_i) - w(d_{\text{alt}}, d_i)) / W_{\text{max}}$
        \item Compute PRI improvement: $\Delta \text{PRI} = \text{PRI}(d_{\text{orig}}) - \text{PRI}(d_{\text{alt}})$
        \item Compute $\text{ARS} = 0.70 \cdot \Delta S + 0.30 \cdot \Delta \text{PRI}$
        \item If ARS $> 0$, add to results
    \end{enumerate}
    \item Sort by ARS descending and return
\end{enumerate}

% ============================================================================
\section{S9: Validation}
% ============================================================================

The ARS framework relies on two independently validated inputs: severity classifications and PRI scores.

\subsection{Severity Classification Validation (DDInter)}

The four-level severity weights were validated against DDInter, an established drug-drug interaction database with curated severity annotations.

\begin{table}[H]
\centering
\caption{DDInter Severity Validation Results}
\label{tab:ddinter_validation}
\begin{tabular}{lc}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Matched DDI Pairs & 6,381 \\
Train/Test Split & 70/30 stratified \\
Exact Accuracy & 71.6\% \\
Adjacent Accuracy & 98.8\% \\
Cohen's $\kappa$ & +0.107 \\
\bottomrule
\end{tabular}
\end{table}

The high adjacent accuracy (98.8\%) ensures that severity rankings are preserved even when exact categories differ.

\subsection{PRI Validation (FAERS)}

The Polypharmacy Risk Index was validated against the FDA Adverse Event Reporting System (FAERS), which serves as real-world ground truth for drug safety signals.

\begin{table}[H]
\centering
\caption{PRI Validation Against FAERS Adverse Event Data}
\label{tab:faers_validation}
\begin{tabular}{lll}
\toprule
\textbf{Metric} & \textbf{Value} & \textbf{Interpretation} \\
\midrule
Sample Size & 87 drugs & Drugs with $\geq$100 FAERS reports \\
Spearman $\rho$ & 0.296 & KG risk vs log(serious event count) \\
95\% CI & [0.090, 0.483] & Bootstrap confidence interval (n=1000) \\
P-value & 0.005 & Statistical significance \\
AUC-ROC & 0.625 & Discriminative ability for high-risk drugs \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Stratified Analysis: PRI Quartiles vs FAERS}

\begin{table}[H]
\centering
\caption{PRI Quartiles vs FAERS Serious Adverse Events}
\label{tab:stratified_validation}
\begin{tabular}{lcccc}
\toprule
\textbf{Risk Quartile} & \textbf{N} & \textbf{Mean PRI} & \textbf{Mean Serious AE} & \textbf{Mean Reports} \\
\midrule
Low & 15 & 0.030 & 8,066 & 10,173 \\
Moderate-Low & 24 & 0.297 & 26,004 & 30,972 \\
Moderate-High & 24 & 0.476 & 38,718 & 49,414 \\
High & 24 & 0.657 & 43,295 & 57,165 \\
\bottomrule
\end{tabular}
\end{table}

The five-fold increase in mean serious adverse events from Low (8,066) to High (43,295) quartile supports PRI as a proxy for real-world pharmacovigilance risk.

\end{document}
